Behavior Driven Development in Haskell

### 2012-06-03 paper.tex
Minor change to abstract
wording.
fixing overflow.
Polish contributions

\begin{abstract}
We observed that several widely used Haskell libraries do not have
tests.
Test code assists developers in maintaining correctness when extending
software, and shows users how an API is supposed to be used.
To ease the production and enhance the value of test code, we advocate
behavior driven development with two tools:
Doctest for user documentation and
Hspec for code documentation.
Our approach can be used for design, documentation and automated
testing.  We hope that this motivates Haskell programmers to write
more and better tests.
\end{abstract}

@@

\begin{itemize}
\item
    We originally implemented Haskell's version of Doctest, and
    extended Haddock's markup to support examples, back in 2010
    (Section~\ref{sec:haddock} and Section~\ref{sec:doctest})
\item
    We added support for QuickCheck properties to Doctest, and extended
    Haddock's markup to support properties
    (Section~\ref{sec:user-doc} and Section~\ref{sec:doctest})

\item
    We introduce a set of combinators to express \emph{expectations} about
    code examples for use with Hspec
    (Section~\ref{sec:code-doc} and Section~\ref{sec:hspec-comb})

\item
    We improve automatic discovery support for Doctest and Hspec
    (Section~\ref{sec:solution-discovery} and Section~\ref{sec:implementation-discovery})

\item
    We show best current practices of BDD in Haskell, using Doctest
    and Hspec (Section~\ref{sec:best-current-practice})

>>>>

\begin{abstract}
We observe that several widely used Haskell libraries do not have
tests.  Test code assists developers in maintaining correctness when
extending software, and shows users how an API is supposed to be used.
To ease the production and enhance the value of test code, we advocate
behavior driven development with two tools: Doctest for user
documentation and Hspec for code documentation.  Our approach can be
used for design, documentation and automated testing.  We hope that
this motivates Haskell programmers to write more and better tests.
\end{abstract}

@@

\begin{itemize}
\item
    We originally implemented Haskell's version of Doctest, and
    extended Haddock's markup to support examples, back in 2010
    (Section~\ref{sec:haddock} and Section~\ref{sec:doctest}).
\item
    We added support for QuickCheck properties to Doctest, and extended
    Haddock's markup to support properties
    (Section~\ref{sec:user-doc} and Section~\ref{sec:doctest}).

\item
    We introduce a set of combinators to express \emph{expectations} about
    code examples for use with Hspec
    (Section~\ref{sec:code-doc} and Section~\ref{sec:hspec-comb}).

\item
    We implemented automatic test discovery for Hspec
    (Section~\ref{sec:solution-discovery} and
    Section~\ref{sec:implementation-discovery}).

\item
    We show best current practices of BDD in Haskell, using Doctest
    and Hspec (Section~\ref{sec:best-current-practice}).
